A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-10-02 bioc-workflow.Rnw
last changes to rnw (not tex) and remove/ammend todos

**TODO** There are other dimensionality reduction methods available in
the \texttt{plot2D} function, which can be parametrised with the
\texttt{method} argument.  Advantages, disadvantages? See
\href{https://gist.github.com/mikelove/74bbf5c41010ae1dc94281cface90d32}
very interesting gist with intriguing tSNE examples. (This might be
better to come after markers.)

@@

\textbf{TODO} Possibly mention \texttt{plot3D} and \texttt{mrkHClust}
(also mentioned later), although these are only available in the
development version.

>>>>

@@

Finally, in addition to \texttt{plot2D}, the \texttt{plot3D} function
allows to interactively explore a 3-dimensional plot of the data.
